Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-04 paper/ms.tex
Move Megan to ack

\author{Megan Bedell}
\affil{\cca}

@@

>>>>

@@

\acknowledgments
We would like to thank David W. Hogg, Kathryn Johnston, and Megan Bedell for
many useful discussions. A.B. would like to thank Todd Phillips for helpful
discussions. A.B. was supported in part by the Roy \& Diana Vagelos Program in
the Molecular Life Sciences and the Roy \& Diana Vagelos Challenge Award. The
work of \Gus{everyone} is supported by the Simons Foundation.
